THESIS PROJECT PROPOSAL

### 2019-11-14 project_ashish/paper.tex
fixed format

\documentclass[final,3p]{CSP}
\usepackage{amssymb}
\usepackage{changepage}
\usepackage{float}
\usepackage{fancyhdr}
%\usepackage[margin=1in,headsep=.2in]{geometry}

\pagestyle{fancy}
\fancyhf{}
\rhead{Thesis Project Proposal}
\lhead{Ashish Sehrawat}
\rfoot{Page \thepage}

\setlength{\headsep}{0.2in}

@@

%\begin{frontmatter}
%\title{THESIS PROJECT PROPOSAL}  
%\author[]{Ashish Sehrawat$^a$}
%\author[]{Dr. Jose Feliciano Benitez Rubio$^b$}
%\cortext[mycorrespondingauthor]{Corresponding author}
%\ead{support@Icm.com}
%\address[mymainaddress]{Universidad de Sonora}
%\begin{keyword}\rm
%\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Keyword:}}  
%Higgs boson, Higgs boson production, Higgs boson decay, Higgs boson coupling, 
%\end{adjustwidth}
%\end{keyword}
%\begin{keyword} \rm
%\end{keyword}
%\begin{abstract}\rm
%\end{abstract}
%\end{frontmatter}

\begin{titlepage}
	\centering
        {\scshape\Large THESIS PROJECT PROPOSAL\par}

	\vspace{2cm}
        \begin{adjustwidth}{2cm}{2cm}{
            TITLE:\par
            \large{Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider}\par}
        \end{adjustwidth}

@@

        \vspace{4cm}
        {\underline{\hspace{8cm}}\par}
	{\scshape\large Ashish Sehrawat\par}
        {Student\par}

        \vspace{1cm}
        {\underline{\hspace{8cm}}\par}
	{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio\par}
        {Director\par}

        \vspace{1cm}
        {Program: Doctorado en Ciencias (F\'{i}sica) \par}
        {Departamento de Investigac\'{i}on en Fis\'{i}ca (DIFUS) \par}
        {Universidad de Sonora \par}

        \vfill
	{\today}

@@

\newpage
{
\hspace{0pt}
\vfill
\centering

  \begin{adjustwidth}{2cm}{2cm}{\large Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider\par}
    \vspace{1cm}
    \centering
    {\itshape\textbf{Abstract:}\par}
    The abstract \par
  \end{adjustwidth}

\hspace{0pt}
\vfill
}

%\centering Ashish Sehrawat
%\newline \newline
%\centering Director: Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio
%\newline \newline
%Posgrado en Ciencias (Fis\'{i}ca)
%\newline 
%Departamento de Investigac\'{i}on en Fis\'{i}ca (DIFUS)
%\newline 
%Universidad de Sonora
%\newline \newline
%\today

\newpage
\section{BACKGROUND}

>>>>

\documentclass[final,3p]{CSP}
\usepackage{amssymb}
\usepackage{changepage}
\usepackage{float}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

\def\Student{Ashish Sehrawat}
\def\Title{THESIS PROJECT PROPOSAL}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider}

%%header and footer
\lhead{\Student}
\rhead{\Title}
\lfoot{\Dept}
\rfoot{Page \thepage}
\setlength{\headsep}{0.2in}
\renewcommand{\footrulewidth}{0.4pt}% default is 0pt

@@

%%%%Title Page
\begin{titlepage}
  \centering
  \hspace{0pt}
  \vfill
        {\scshape\Large \Title \par}

	\vspace{2cm}
        \begin{adjustwidth}{2cm}{2cm}{
            TITLE:\par
            {\large \ProjectTitle \par}
          }
        \end{adjustwidth}

@@

        \vspace{4cm}
        {\underline{\hspace{8cm}}\par}
	{\scshape\large \Student \par}
        {Student\par}

        \vspace{1cm}
        {\underline{\hspace{8cm}}\par}
	{\Director \par}
        {Director\par}

        \vspace{1cm}
        {\Prog \par}
        {\Dept \par}
        {Universidad de Sonora \par}

        \vspace{4cm}
	{\today}

\hspace{0pt}
\vfill

@@

%%%%% white page for print out
\shipout\null

%%%% Abstract Page
\newpage
\hspace{0pt}
\vfill

\begin{adjustwidth}{1cm}{1cm}

  \begin{center}
    {\Large \ProjectTitle \par}
    \vspace{1cm}
    {\itshape\textbf{Abstract}\par}
  \end{center}

  The abstract \par

\end{adjustwidth}

\hspace{0pt}
\vfill

%%%%%% Begin the body
\newpage
\section{BACKGROUND}
